### 2019-04-08 paper/paper.tex
some updates

\section{Methodology}
% CHECK IF THE NUMBERS ARE RIGHT
The window of data observed within this paper is October 1\textsuperscript{st} 2010 (as in the original paper) to April 1\textsuperscript{st} 2019.
We collected from three publicly available data sets. Two of these, the \code{npm} registry and the \code{GitHub} repository platform, are from the same source as in the original paper.
To find repositories relying \code{npm}, we used the Google BigQuery \code{github\_repos} data set, updated weekly\footnote{https://github.com/fhoffa/analyzing\_github/}.
By using this set we are able to analyze \code{GitHub} data without being constrained to the currently available window provided by the GHTorrent project\cite{ghtorrent}.
The final data set encompasses 797,940 packages and TODO:FILL applications.

\subsection{Data Collection}

@@

@@

@@

  \bibitem{Wittern:2016:LDJ:2901739.2901743}

>>>>

\section{Data Collection}
% CHECK IF THE NUMBERS ARE RIGHT
The window of data analyzed within this paper is October 1\textsuperscript{st} 2010 (as in the original paper) to April 1\textsuperscript{st} 2019.
We collected from three publicly available data sets. Two of these, the \code{npm} registry and the \code{GitHub} repository platform, are from the same source as in the original paper.
To find repositories relying \code{npm}, we used the Google BigQuery \code{github\_repos} data set, updated weekly\footnote{https://github.com/fhoffa/analyzing\_github/}.
By using this set we are able to analyze \code{GitHub} data without being constrained to the currently available window provided by the GHTorrent project\cite{ghtorrent}.
The final data set encompasses 797,940 packages and \textbf{\#VALUE} applications.

@@

\textbf{this one is probably mostly for @Fred}

@@

\textbf{@Greg I'm gonna need you to put something here}

@@
